% !TEX encoding = UTF-8 Unicode
% !TEX program = lualatex
% !TEX spellcheck = English


\documentclass{article}
    \parindent0pt
    \parskip10pt plus10pt
    \def\email#1{\href{mailto:#1}{#1}}
    \def\section#1{$ $\\\textbf{\fs1#1}}

\usepackage[margin=86pt]{geometry}

\usepackage{fontspec}
    \setmainfont[ItalicFont=NotoSerif-Italic,
                   BoldFont=NotoSerif-Bold]
                           {NotoSerif}
    \setsansfont           {NotoSerif}%{NotoSans}
    \setmonofont           {NotoSerif}%{NotoSansMono-Regular}
    \newfontfamily\zhfamily{STSongti-TC-Regular}

\usepackage{pgfmath}
    \def\fs#1{%
        \pgfmathsetmacro\a{#1}%
        \pgfmathsetmacro\A{10 * 1.2^\a}%
        \pgfmathsetmacro\B{\A * 1.25}%
        \fontsize{\A pt}{\B pt}\selectfont%
    }

\usepackage{xcolor, xurl, hyperref}
    \hypersetup{colorlinks, allcolors=blue!50!purple}

\begin{document}

\leftskip0pt plus1fill
\rightskip0pt plus1fill

                                 \title
                           {Curriculum Vitae}

                                \author
                           {Hsin-Po Wang 王新博}

\fs2

                            CURRICULUM VITAE

                    Hsin-Po Wang ~ ~ {\zhfamily 王新博}

\fs0

                Website: \url{https://www.symbol.codes}
                                   \\
                Email: \email{a.simple.people@gmail.com}
                                   \\
                            Google Scholar:
      \url{https://scholar.google.com/citations?user=tJ8-ChgAAAAJ}

\leftskip0pt
\rightskip0pt
\fs0

\section{Education}

Ph.D in Math
\hfill University of Illinois Urbana-Champaign, Illinois
\hfill 2016--2021

BSc in Math
\hfill National Taiwan University ({\zhfamily 國立臺灣大學}), Taiwan
\hfill 2011--2015

\section{Employment}

Apple Research Fellow                        \hfill January--May 2024 \\
Simons Institute for the Theory of Computing, California

Postdoctoral Scholar               \hfill October 2022--December 2023 \\
Department of Electrical Engineering and Computer Sciences, \\
University of California, Berkeley, California

Postdoctoral Scholar              \hfill October 2021--September 2022 \\
Department of Electrical and Computer Engineering, \\
University of California San Diego, California

Teaching Assistant                    \hfill September 2016--May 2023 \\
Department of Mathematics,  
University of Illinois Urbana-Champaign, Illinois

\section{Awards and Honors}

Irving Reiner Memorial Award in Algebra                      \hfill 2021

Research Assistant Fellowship                         \hfill Spring 2020

Teacher ranked as excellent by their students
                              \hfill Fall 2019, Spring 2019, Spring 2018

Book--Scroll Award (top 5\% GPA)
       \hfill Fall 15, Spring 14, Spring 13, Fall 12, Spring 12, Fall 11

Prof. Cheng-Tang Hsiao Memorial Scholarship ({\zhfamily 蕭正堂紀念獎學金})
                                                             \hfill 2014

Prof. Ta-Kai Hu Memorial Scholarship ({\zhfamily 胡達開先生紀念獎學金})
                                                             \hfill 2013

\section{Research Interests}

Information theory
• Coding theory
• Polar codes (wireless communication)
• Distributed storage and distributed computation
• Group testing
• Applications of algebra, combinatorics, calculus, probability theory
  and other mathematics tools

\section{Peer-Reviewed Conference Publications (New to Old)}

\bgroup
\def\section#1#2{}
\begin{thebibliography}{9}
    \bibitem{}
    H.-P. Wang, R. Gabrys, V. Guruswami.
    \emph{Quickly-Decodable Group Testing with Fewer Tests:
    Price-Scarlett's Nonadaptive Splitting with Explicit Scalars}.
    IEEE International Symposium on Information Theory (ISIT).
    June 2023.
    \url{https://doi.org/10.1109/ISIT54713.2023.10206843}

    \bibitem{}
    H.-P. Wang, C.-W. Chin.
    \emph{Density Devolution for Ordering Synthetic Channels}.
    IEEE International Symposium on Information Theory (ISIT).
    June 2023.
    \url{https://doi.org/10.1109/ISIT54713.2023.10206540}

    \bibitem{}
    T.-C. Lin, H.-P. Wang.
    \emph{Optimal Self-Dual Inequalities to Order Polarized BECs}.
    IEEE International Symposium on Information Theory (ISIT).
    June 2023.
    \url{https://doi.org/10.1109/ISIT54713.2023.10206451}
    
    \bibitem{}
    H.-P. Wang, V. Guruswami.
    \emph{How Many Matrices Should I Prepare to Polarize Channels
    Optimally Fast?}
    IEEE International Symposium on Information Theory (ISIT).
    June 2023.
    \url{https://doi.org/10.1109/ISIT54713.2023.10206989}

    \bibitem{}
    H.-P. Wang, V.-F. Dragoi.
    \emph{Fast Methods for Ranking Synthetic BECs}.
    IEEE International Symposium on Information Theory (ISIT).
    June 2023.
    \url{https://doi.org/10.1109/ISIT54713.2023.10206704}

    \bibitem{}
    I. Duursma, R. Gabrys, V. Guruswami, T.-C. Lin, H.-P. Wang.
    \emph{Accelerating Polarization via Alphabet Extension}.
    International Conference on Randomization and Computation (RANDOM).
    September 2022.
    \url{https://doi.org/10.4230/LIPIcs.APPROX/RANDOM.2022.17}

    \bibitem{}
    H.-P. Wang, R. Gabrys, A. Vardy.
    \emph{PCR, Tropical Arithmetic, and Group Testing}.
    IEEE International Symposium on Information Theory (ISIT).
    June 2022.
\url{https://doi.org/10.1109/ISIT50566.2022.9834718}
\end{thebibliography}
\egroup

\section{Journal Publications (New to Old)}

\bgroup
\def\section#1#2{}
\begin{thebibliography}{9}
    \bibitem{}
    H.-P. Wang and R. Gabrys and A. Vardy.
    \emph{Tropical Group Testing}.
    IEEE Transactions on Information Theory.
    June 2023.
    \url{https://ieeexplore.ieee.org/document/10146331/}

    \bibitem{}
    H.-P. Wang, T.-C. Lin, A. Vardy, R. Gabrys.
    \emph{Sub-4.7 Scaling Exponent of Polar Codes}.
    IEEE Transactions on Information Theory.
    March 2023
    \url{https://doi.org/10.1109/TIT.2023.3253074}

    \bibitem{}
    I. Duursma, H.-P. Wang.
    \emph{Multilinear Algebra for Minimum Storage Regenerating Codes:
        A Generalization of Product-Matrix Construction}.
    Applicable Algebra in Engineering, Communication and Computing.
    October 2021.
    \url{https://doi.org/10.1007/s00200-021-00526-3}

    \bibitem{}
    I. Duursma, X. Li, H.-P. Wang.
    \emph{Multilinear Algebra for Distributed Storage}.
    SIAM Journal on Applied Algebra and Geometry (SIAGA).
    September 2021.
    \url{https://doi.org/10.1137/20M1346742}

    \bibitem{}
    H.-P. Wang, I. Duursma.
    \emph{Log-logarithmic Time Pruned Polar Coding}.
    IEEE Transactions on Information Theory.
    March 2021.
    \url{https://doi.org/10.1109/TIT.2020.3041523}

    \bibitem{}
    H.-P. Wang, I. Duursma.
    \emph{Polar Codes' Simplicity, Random Codes' Durability}.
    IEEE Transactions on Information Theory.
    March 2021.
    \url{https://doi.org/10.1109/TIT.2020.3041570}
\end{thebibliography}
\egroup

\section{Invited Talk}

\bgroup
\def\section#1#2{}
\begin{thebibliography}{9}
    \bibitem{}
    H.-P. Wang.
    \emph{Channel Manipulation as a Coding Technique}.
    Joint Mathematics Meetings (JMM).
    January 2024.
    \url{https://meetings.ams.org/math/jmm2024/meetingapp.cgi/Paper/29146}
\end{thebibliography}
\egroup

\end{document}
